An Interpretable Machine Learning Framework for Modeling High-Resolution Spectroscopic Data\footnote{Open source code at \url{https://github.com/gully/blase}}

### 2022-10-03 paper/paper1/ms.tex
Some changes to get the arxiv version to render

\begin{acknowledgments}

    We thank the anonymous referee for comments that improved the paper.  We thank Phill Cargile, Hajime Kawahara, and Dan Jaffe for pre-print comments that were incorporated into the draft text.
    MGS thanks Ian Czekala, Phill Cargile, Rodrigo Luger, Greg Herczeg, Will Best, Dan Foreman-Mackey, Meg Bedell, Mark Marley, Erwan Pannier, Dirk C.M. van den Bekerom, Dan Clemens, Dan Jaffe, Tom Greene, Adam Kraus, David Hogg, Greg Zeimann, Ben Montet, Christina Hedges, Brittany Miles, Arpita Roy, and Kevin Gullikson for conversations and resources that shaped his thinking on spectral calibration and telluric mitigation.

@@

    This research has made use of NASA's Astrophysics Data System Bibliographic Services.

\end{acknowledgments}

>>>>

\pagebreak
\newpage

\begin{acknowledgments}
    \footnotesize{
        We thank the anonymous referee for comments that improved the paper.  We thank Phill Cargile, Hajime Kawahara, and Dan Jaffe for preprint comments.

@@

        MGS thanks Ian Czekala, Phill Cargile, Rodrigo Luger, Greg Herczeg, Will Best, Dan Foreman-Mackey, Meg Bedell, Mark Marley, Erwan Pannier, Dirk C.M. van den Bekerom, Dan Clemens, Dan Jaffe, Tom Greene, Adam Kraus, David Hogg, Greg Zeimann, Ben Montet, Christina Hedges, Brittany Miles, Arpita Roy, and Kevin Gullikson for conversations and resources that shaped his thinking on spectral calibration and telluric mitigation.
    }
\end{acknowledgments}
